### 2013-08-23 doc/dissertation/document/frontmatter/acks.tex
updating acks

>>>>

Great thanks are owed to my advisor and friend Paul Wilson for
graciously giving me years of guidance and the opportunity to develop
this work. He provided me with both the resources and challenges to
grow as a researcher. Without his influence and support, this work
would have never been possible.

Tom Evans is responsible for presenting me with the seeds of this work
and for that I thank him. His mentoring over the past few years has
been invaluable and the skills and lessons I have learned from him
have proven indispensable.

Roger Pawlowski and other members of the Consortium for Advanced
Simulation of Light Water Reactors and Trilinos teams as well as many
staff members at Oak Ridge National Laboratory have provided
tremendous resources for my professional and technical development and
have greatly facilitated this work.
